Beliefs about the development of mental life

### 2025-02-14 paper/paper_anonymized.Rmd
revisions for R&R

Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (anonymized links for peer review, Study 1: \url{https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34}; Study 2: \url{https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18}; Study 3: \url{https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4)}). All studies were approved by [IRB information omitted for anonymous review]. For extended descriptions of methods and results, see Supplemental Materials.

@@

Following recent work on mind perception [@weisman.etal2021], our goal in this analysis was to derive a set of latent constructs that together give rise to people's intuitions about the development of human mental life between 0-5 years. We did not set out to sort each of the 60 capacities into discrete, non-overlapping categories of capacities. Instead, we understood each of these specific capacities to reflect a different combination of the same underlying components (much as specific colors of paint can be understood as different combinations of cyan, magenta, and yellow). This theoretical perspective motivated our choice of exploratory factor analysis as our dimensionality reduction technique (rather than, e.g., principal components analysis or cluster analysis); our choice of labels for each factor, in which we have attempted to describe what might be understood by participants as core components of the developing human mind (rather than attempting to label a category); and our interpretation of factor loadings, which focuses not only on capacities that load strongly on only one factor but also on capacities that cross-load on multiple factors. See Supplemental Materials for more details about this analysis, including our decision to treat participants' ratings of each of the three target ages as if they were a distinct source of data.

A `r s1_results$efa$factors`-factor solution (as suggested by parallel analysis) accounted for `r round_x(s1_results$efa$Vaccounted["Cumulative Var", "MR4"]*100, 0)`% of the total variance in participants' capacity attributions, suggesting that four latent constructs can account for a substantial amount of the variability across target ages and across individual participants in perceptions of infants' and young children's mental lives. See Figure 1 for all factor loadings after oblique transformation. [See also Supplemental Materials for the 8-factor solution suggested by minimizing BIC, and the 2-factor solution suggested by implementing the factor retention criteria employed in @weisman.etal2017a.]

@@

Regressing participants' item-level responses onto target age, domain, and interactions between them via a multilevel generalized additive model (using a binomial distribution and the logit link function) confirmed both of our preregistered hypotheses: On average, participants rated older children as more capable, but perceptions of the development of children's capacities differed dramatically across domains. Modeling the effects of target age via smoothing terms allowed us to reconstruct the shape these perceived developmental trajectories from the bottom up (see Figure 2), without specifying in advance the shape of the curve.

@@

Responses to questions about developmental mechanisms are visualized in Figure 3.

@@

In terms of selections of the "most important" mechanism driving the development of these capacities between 0-5 years, two explanations—biological preprogramming and brain changes—accounted for most of participants' selections. Percentage selections and modal responses for all developmental mechanisms are presented in Figure 3. (See also Supplemental Materials for a multinomial regression comparing the selection of most important mechanism across capacities.)

@@

Independent ratings of the importance of each developmental mechanism present a more nuanced—but largely consistent—picture of intuitive theories of development across these domains. See Figure 3, and see Supplemental Materials for the full results of the multilevel linear regression analyses briefly presented below.

@@

For capacities in the domain that we have called _bodily sensation_ (Figure 3, top row), "the child is biologically 'preprogrammed' to have this ability" stood out as the highest-rated mechanism by far (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`), followed by "the child's brain changes " (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`), and "the child's body grows and matures" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p), 3)))`). The remaining mechanisms were rated as quite unimportant for capacities in this domain (all medians $\leq$ `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-7, median) %>% top_n(1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`; all $M$ $\leq$ `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-7, mean) %>% top_n(1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`), with particularly low ratings for "people explicitly teach the child how to do this" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p), 3)))`).

>>>>

Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (anonymized links for peer review, Study 1: \url{https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34}; Study 2: \url{https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18}; Study 3: \url{https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4)}). All studies were approved by [IRB information omitted for anonymous review]. For extended descriptions of methods and results, see Supplemental Materials. Note: scripts for all analyses, figures, and tables are available in the .Rmd file that generated the fully reproducible Supplemental Materials document (supplement-main.Rmd), which can be found in the following GitHub repository (anonymized for peer review): \url{https://anonymous.4open.science/r/baby_mental_life_ms-C261/}.

@@

Following recent work on mind perception [@weisman.etal2021], our goal in this analysis was to derive a set of latent constructs that together give rise to people's intuitions about the development of human mental life between 0-5 years. We did not set out to sort each of the 60 capacities into discrete, non-overlapping categories of capacities. Instead, we understood each of these specific capacities to reflect a different combination of the same underlying components (much as specific colors of paint can be understood as different combinations of cyan, magenta, and yellow). This theoretical perspective motivated our choice of exploratory factor analysis as our dimensionality reduction technique (rather than, e.g., principal components analysis or cluster analysis); our choice of labels for each factor, in which we have attempted to describe what might be understood by participants as core components of the developing human mind (rather than attempting to label a category); and our interpretation of factor loadings, which focuses not only on capacities that load strongly on only one factor but also on capacities that cross-load on multiple factors. See Supplemental Materials for more details about this analysis, including our decision to treat participants' ratings of each of the three target ages as if they were a distinct source of data, and solutions employing orthogonal (varimax) rotation rather than the oblique (oblimin) transformations presented here.

A `r s1_results$efa$factors`-factor solution (as suggested by parallel analysis) accounted for `r round_x(s1_results$efa$Vaccounted["Cumulative Var", "MR4"]*100, 0)`% of the total variance in participants' capacity attributions, suggesting that four latent constructs can account for a substantial amount of the variability across target ages and across individual participants in perceptions of infants' and young children's mental lives. See Figure 1 for all factor loadings after oblique transformation, and see Supplemental Materials for a scatterplot matrix ("pairs plot") and related plots visualizing the relationships among factor loadings across these four factors and the distributions of factor loadings across items (Figures S1-S7); as well as factor loading for the 8-factor solution suggested by minimizing BIC, and the 2-factor solution suggested by implementing the factor retention criteria employed in Weisman et al. (2017).

@@

Regressing participants' item-level responses onto target age, domain (assigned a priori; see preregistration), and interactions between them via a multilevel generalized additive model (using a binomial distribution and the logit link function) confirmed both of our preregistered hypotheses: On average, participants rated older children as more capable, but perceptions of the development of children's capacities differed dramatically across domains. Modeling the effects of target age via smoothing terms allowed us to reconstruct the shape of these perceived developmental trajectories from the bottom up (see Figure 2), without specifying in advance the shape of the curve.

@@

Responses to questions about developmental mechanisms are visualized in Figures 3 and 4.

@@

In terms of selections of the "most important" mechanism driving the development of these capacities between 0-5 years, two explanations—biological preprogramming and brain changes—accounted for most of participants' selections. Percentage selections and modal responses for all developmental mechanisms are presented in Figure 3; a network graph summarizing the importance of each developmental mechanism for each capacity is presented in Figure 4. (See also Supplemental Materials for a multinomial regression comparing the selection of the most important mechanism across capacities.)

@@

Independent ratings of the importance of each developmental mechanism present a more nuanced—but largely consistent—picture of intuitive theories of development across these domains. See Figures 3-4, and see Supplemental Materials for the full results of the multilevel linear regression analyses briefly presented below.

@@

For capacities in the domain that we have called _bodily sensation_ (Figure 3, top row; Figure 4, first and second capacities from the left), "the child is biologically 'preprogrammed' to have this ability" stood out as the highest-rated mechanism by far (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`), followed by "the child's brain changes " (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`), and "the child's body grows and matures" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p), 3)))`). The remaining mechanisms were rated as quite unimportant for capacities in this domain (all medians $\leq$ `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-7, median) %>% top_n(1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`; all $M$ $\leq$ `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-7, mean) %>% top_n(1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`), with particularly low ratings for "people explicitly teach the child how to do this" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p), 3)))`).

For capacities in the domain of _negative affect_ (Figure 3, second row; Figure 4, third and fourth capacities from the left), the two highest-rated mechanisms were again "the child is biologically 'preprogrammed' to have this ability" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`) and "the child's brain changes " (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`). However, these two biologically inflected explanations were closely followed by explanations that are more social and observational in nature: "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`); "the child observes objects and the physical world" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(p), 3)))`); "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`). The remaining mechanisms were rated as fairly unimportant for capacities in this domain (median scores: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(-1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(-5, median) %>% top_n(1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`; means: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(-1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(-5, mean) %>% top_n(1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`).
